Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-05-10 papers/paper_alt_theor_bounds/arxiv_v1/paper_alt_theor_bounds.tex
hs: removed comment and continuous-line abstract for arxiv

In the end, the $\pSEOB$ waveform model with theory-specific
QNMs has only $\ell_{\rm th}$ as a free beyond-GR parameter.
%
We emphasize that our procedure is different from that of
Ref.~\cite{Carullo:2021dui} which, for a given value of $p$, varied all $\ell_{\rm th}$,
$\delta\omega^{(j)}$, and $\delta\tau^{(j)}$ parameters, and then proceeded
to use the posteriors on $\ell_{\rm th}$, considering up to $j=2$ in
the GR deformation coefficients, and remaining agnostic about the underlying
theory which would predict the modifications to the QNMs.
%
\hs{We will see in Sec.~\ref{sec:results} that} adding theory-specific
information to the ParSpec coefficients \emph{can lead to different interpretations
of the bounds on $\ell_{\rm th}$, even for different theories that predict the same
value of the exponent $p$.}

@@

In this theory, we have considered only $N_{\rm max} = 0$.
%
We find that the addition of spin corrections (while maintaining the same prior
ranges on $\ell_{\rm qEFT}$ as used in the $N_{\rm max} = 0$ study) can result
in waveforms that can have a ringdown segment larger (sometimes seconds long)
than the inspiral-plunge segment in the detectors' frequency band, making the
parameter estimation challenging.
%
To overcome this issue we have lowered the value of $\ell^{\rm max}_{\rm qEFT}$, but by doing so we have obtained posteriors
which were flat, just as our prior, and were thus uninformative. Hence, we do not quote any results for $N_{\rm max} = 1$.
%
Table~\ref{tab:summary_qeft} summarizes our findings for the quartic EFT of GR.
%
\begin{figure}[t]
\includegraphics[width=\columnwidth]{figs/qeft_posteriors_combined.pdf}
\caption{(Color online).~Similar to Fig.~\ref{fig:edgb_exec_sum}, but for the quartic EFT of GR.
We show our results for GW150914 (top panel), GW200129 (middle panel) and combined events (bottom panel).
%
As there, we mark with the vertical lines the 90\% upper credible intervals.
}
\label{fig:qEFT_exec_sum}
\end{figure}

\begin{figure}[t]
\includegraphics[width=\columnwidth]{figs/qeft_cdf_varying_threshold.pdf}
\caption{Similar to Fig.~\ref{fig:edgb_cdf}, but for the quartic EFT of GR.
We find that similarly to what happens in dCS gravity and the cubic EFT of GR, we
can place a constrain on $\ell_{\rm qEFT}$ when $\gm = M_{\rm f}$ for both events at 68\% credibility.
}
\label{fig:qEFT_cdf}
\end{figure}

@@

\begin{figure*}[t]
\includegraphics[width=0.9\textwidth]{figs/tmp_GW150914_intrinsic_params.pdf}
\caption{(Color online).~Corner plot showing that the inferred source binary parameters for GW150914,
using the same waveform model \pSEOB, but with (purple contours) and without setting the non-GR parameters different
from zero (blue contours), having as an illustrative example dCS gravity and $N_{\rm max}=0$.
%
Here, $\chi_{\rm eff}$ is the dimensionless effective-spin parameter, related to the individual spins $\chi_{i}$
and masses $m_{i}$ of each binary component as $\chi_{\rm eff} \equiv (m_1 \chi_1 + m_2 \chi_2) / (m_1 + m_2)$.
%
All contours correspond to 90\% credible levels.
%
We see that the addition of the non-GR parameters does not introduce biases in the
inference of the source parameters.
%
We found the same qualitative behavior in the posteriors distributions of the
source binary parameters for the other modified gravity theories studied in the
main text.
%
The same conclusions apply for the other GW event studied here, GW200129.
}
\label{fig:corner_plot_all}
\end{figure*}

>>>>

In the end, the $\pSEOB$ waveform model with theory-specific
QNMs has only $\ell_{\rm th}$ as a free beyond-GR parameter.
%
We emphasize that our procedure is different from that of
Ref.~\cite{Carullo:2021dui} which, for a given value of $p$, varied all $\ell_{\rm th}$,
$\delta\omega^{(j)}$, and $\delta\tau^{(j)}$ parameters, and then proceeded
to use the posteriors on $\ell_{\rm th}$, considering up to $j=2$ in
the GR deformation coefficients, and remaining agnostic about the underlying
theory which would predict the modifications to the QNMs.
%
We will see in Sec.~\ref{sec:results} that adding theory-specific
information to the ParSpec coefficients \emph{can lead to different interpretations
of the bounds on $\ell_{\rm th}$, even for different theories that predict the same
value of the exponent $p$.}

@@

In this theory, we have considered only $N_{\rm max} = 0$.
%
We find that the addition of spin corrections (while maintaining the same prior
ranges on $\ell_{\rm qEFT}$ as used in the $N_{\rm max} = 0$ study) can result
in waveforms that can have a ringdown segment larger (sometimes seconds long)
than the inspiral-plunge segment in the detectors' frequency band, making the
parameter estimation challenging.
%
To overcome this issue we have lowered the value of $\ell^{\rm max}_{\rm qEFT}$, but by doing so we have obtained posteriors
which were flat, just as our prior, and were thus uninformative. Hence, we do not quote any results for $N_{\rm max} = 1$.
%
Table~\ref{tab:summary_qeft} summarizes our findings for the quartic EFT of GR.
%
\begin{figure}[t]
\includegraphics[width=\columnwidth]{qeft_posteriors_combined.pdf}
\caption{(Color online).~Similar to Fig.~\ref{fig:edgb_exec_sum}, but for the quartic EFT of GR.
We show our results for GW150914 (top panel), GW200129 (middle panel) and combined events (bottom panel).
%
As there, we mark with the vertical lines the 90\% upper credible intervals.
}
\label{fig:qEFT_exec_sum}
\end{figure}

\begin{figure}[t]
\includegraphics[width=\columnwidth]{qeft_cdf_varying_threshold.pdf}
\caption{Similar to Fig.~\ref{fig:edgb_cdf}, but for the quartic EFT of GR.
We find that similarly to what happens in dCS gravity and the cubic EFT of GR, we
can place a constrain on $\ell_{\rm qEFT}$ when $\gm = M_{\rm f}$ for both events at 68\% credibility.
}
\label{fig:qEFT_cdf}
\end{figure}

@@

\begin{figure*}[t]
\includegraphics[width=0.9\textwidth]{GW150914_intrinsic_params.pdf}
\caption{(Color online).~Corner plot showing that the inferred source binary parameters for GW150914,
using the same waveform model \pSEOB, but with (purple contours) and without setting the non-GR parameters different
from zero (blue contours), having as an illustrative example dCS gravity and $N_{\rm max}=0$.
%
Here, $\chi_{\rm eff}$ is the dimensionless effective-spin parameter, related to the individual spins $\chi_{i}$
and masses $m_{i}$ of each binary component as $\chi_{\rm eff} \equiv (m_1 \chi_1 + m_2 \chi_2) / (m_1 + m_2)$.
%
All contours correspond to 90\% credible levels.
%
We see that the addition of the non-GR parameters does not introduce biases in the
inference of the source parameters.
%
We found the same qualitative behavior in the posteriors distributions of the
source binary parameters for the other modified gravity theories studied in the
main text.
%
The same conclusions apply for the other GW event studied here, GW200129.
}
\label{fig:corner_plot_all}
\end{figure*}
